Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-19 ms.tex
slight edit of conclusion to clean up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
\label{ss:offset}

\citet{gorman2013}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{}

@@

The radio emission due to the interaction between the planetary companion and the stellar wind would be brighter than the intrinsic radio emission from the host star.

The candidate radio detectors sensitive to the radio emission from 10~MHz to 1~GHz are LWA are SKA. For LWA,

This is above the detection limit of the

Non-detection

For planets around AGB stars, be
, which provides us to

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
\label{ss:offset}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

-about detectability
-number of evolved stars within 100pc $\sim 1000$.
